\mytitle

### 2012-03-02 papers/SAS2012/implicitization.tex
path

\cite{Monniaux_Gonnord_SAS11}'s \emph{path-focusing} technique
distinguishes the different paths in the program in order to avoid loss of
precision due to merge operations. Since the number of paths may be exponential,
the technique keeps them implicit and computes them when needed using
SMT-solving.
The (accelerated) Kleene iterations (\S\ref{sec:static_analysis}) are computed over a reduced multigraph instead of the classical transition graph.

@@

\cite{DBLP:conf/pldi/GulwaniZ10} proposed a technique for computing disjunctive invariants, by
distinguishing all the paths inside a loop. In
this section, we propose to improve this technique by using SMT queries to find
interesting paths, the objective being to avoid an explicit exhaustive
enumeration of an exponential number of paths.

>>>>

Monniaux \& Gonnord's \emph{path-focusing} \cite{Monniaux_Gonnord_SAS11} technique
distinguishes the different paths in the program in order to avoid loss of
precision due to merge operations. Since the number of paths may be exponential,
the technique keeps them implicit and computes them when needed using
SMT-solving.
The (accelerated) Kleene iterations (\S\ref{sec:static_analysis}) are computed over a reduced multigraph instead of the classical transition graph.

@@

Gulwani \& Zuleger \cite{DBLP:conf/pldi/GulwaniZ10} proposed a technique for computing disjunctive invariants, by
distinguishing all the paths inside a loop. In
this section, we propose to improve this technique by using SMT queries to find
interesting paths, the objective being to avoid an explicit exhaustive
enumeration of an exponential number of paths.
